Evolution of Methodologies in Delivering Reliable Software in the European Scientific Arena

### 2018-06-01 paper-ieee-trans.tex

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth, height=50mm]{images/fig3.png}
\caption{Trend line showing the adoption of Configuration Management tools throughout the project lifetime.}
\label{fig:fig_confman}
\end{figure}

@@

\item \textit{Automated Deployment}.
To lower the barriers of software adoption, the SQA criteria require the automated
deployment of the products delivered as part of the catalogue. Automation in this context is
tackled using a configuration management tool. These tools allow to have an
\textit{Infrastructure as Code} (IaC), managing the component's deployment through declarative
definitions. The definition files appear as additional source of documentation
-- self--documenting code -- as they sequentially guide the component's deployment process in multiple
platforms. {\sl INDIGO--DataCloud} project contributed to open--source IaC tools such
as Ansible \cite{indigo-ansible} and Puppet \cite{indigo-puppet}. A representative example of
such contribution are the \textit{50 roles} being developed from scratch, currently hosted in
the Ansible Galaxy portal \cite{indigo-galaxy}. Fig.~\ref{fig:fig_confman}
shows the number of products that offer an automated means for deployment.
It shows an increase after the {\sl INDIGO--1} release and in the previous weeks of each
of the two major releases.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
% Duplicate
\bibitem{indigo-ansible}
\emph{INDIGO--DataCloud Ansible Galaxy repository} [Online]. Available:
https://galaxy.ansible.com/indigo-dc/ .

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
% Duplicate
\bibitem{ggus}
\emph{Global Grid User Support (GGUS)} [Online]. Available: https://www.ggus.eu/

>>>>

\begin{figure*}[ht]
\centering
\includegraphics[width=0.8\textwidth]{images/fig3.png}
\caption{Trend line showing the adoption of Configuration Management tools throughout the project lifetime.}
\label{fig:fig_confman}
\end{figure*}

@@

\item \textit{Automated Deployment}.
To lower the barriers of software adoption, the SQA criteria require the automated
deployment of the products delivered as part of the catalogue. Automation in this context is
tackled using a configuration management tool. These tools allow to have an
\textit{Infrastructure as Code} (IaC), managing the component's deployment through declarative
definitions. The definition files appear as additional source of documentation
-- self--documenting code -- as they sequentially guide the component's deployment process in multiple
platforms. {\sl INDIGO--DataCloud} project contributed to open--source IaC tools such
as Ansible \cite{indigo-galaxy} and Puppet \cite{indigo-puppet}. A representative example of
such contribution are the \textit{50 roles} being developed from scratch, currently hosted in
the Ansible Galaxy portal \cite{indigo-galaxy}. Fig.~\ref{fig:fig_confman}
shows the number of products that offer an automated means for deployment.
It shows an increase after the {\sl INDIGO--1} release and in the previous weeks of each
of the two major releases.
\end{itemize}

@@

@@
